rotation_runs2019

### 2020-02-12 inst/documents/paper_figs_rotations201911.Rmd
paper fig edits

@@

```{r fig1-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

@@

```{r fig2-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

@@

# A3 frequency switch insecticides same, no costs, disp
# in this example rotations have a reasonable advantage but I'm not sure why !!

```{r fig3-examp-run-A3, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0026, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE )

@@

```{r fig4-examp-run-B2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#in sequence first insecticide keeps being used for 500 gen
#in rotation switch to other insecticides that reach thereshold means that generations are lost over threshold

dfseq <- run_rot(n_insecticides=3, start_freqs=0.093, cost=c(0.07,0.067,0.032), eff=c(0.8,0.79,0.71),
dom_sel=c(0.23,0.68,0.38), dom_cos=c(0.89,0.65,0.55), rr=c(0.12,0.75,0.33), expo_hi=0.73, male_expo_prop=0.25, coverage=1, migration=0, min_rwr_interval=10)

>>>>

#fig1 before this is model description

@@

```{r fig2-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.001, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.001, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE  )

@@

```{r fig3-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.001, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.001, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE  )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE  )

@@

# C2 mortality switch insecticides same, no costs, disp

```{r fig4-examp-run-C2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# mortality switch

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.001, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'mort')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.001, cost=c(0.02), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=1, migration=0,
min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'mort')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE  )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE  )

# A3 frequency switch insecticides same, no costs, disp

```{r fig5-examp-run-A3, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.001, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.001, cost=c(0), eff=c(0.98), dom_sel=c(0.96), dom_cos=c(0.32), rr=c(0.12), expo_hi=0.75, male_expo_prop=0.34, coverage=0.3, migration=0.1, min_rwr_interval=10, plot=FALSE, max_gen=500, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE, logy =FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE, logy =FALSE )

@@

```{r fig6-examp-run-B2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#in sequence first insecticide keeps being used for 500 gen
#in rotation switch to other insecticides that reach threshold means that generations are lost over threshold

dfseq <- run_rot(rot_interval=0, n_insecticides=3, start_freqs=0.0059, cost=c(0.099,0.088,0.062), eff=c(1,0.96,0.78), dom_sel=c(0.63,0.95,0.42), dom_cos=c(0.6,0.49,0.14), rr=c(0.36,0.11,0.86), expo_hi=0.65, male_expo_prop=0.087, coverage=1, migration=0, plot=FALSE, max_gen=500, change_interval=10, mort_or_freq = 'freq')

dfrot <- run_rot(rot_interval=10, n_insecticides=3, start_freqs=0.0059, cost=c(0.099,0.088,0.062), eff=c(1,0.96,0.78), dom_sel=c(0.63,0.95,0.42), dom_cos=c(0.6,0.49,0.14), rr=c(0.36,0.11,0.86), expo_hi=0.65, male_expo_prop=0.087, coverage=1, migration=0, plot=FALSE, max_gen=500, change_interval=10, mort_or_freq = 'freq')

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=FALSE, plot_refuge = FALSE, logy =FALSE )

### 2020-02-12 inst/documents/rotation_runs2019.Rmd
paper fig edits

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

>>>>

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B1'
#id_expt <- 'B2'
#id_expt <- 'B3'
id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'
